Lawvere-Tierney Sheafification in Homotopy Type Theory

### 2016-04-06 paper/paper_lipics.tex
foo

%
This restriction in our formalization may be solved by
generalizing the management of universe polymorphism for recursive definition
%
or by the use of general ``resizing axiom'' which is still under
discussion in the community.

>>>>

%
This restriction in our formalization may be solved by
generalizing the management of universe polymorphism for recursive definition
%
or by the use of general ``resizing axiom'' which is still under
discussion in the community.
%
We note that for this solution to work, we need to have a slighlty
weaker definition of modalities than the one in~\cite{hottlib}. We
usually ask the reflector $\modal$ to map a universe $\Type^i$ to
itself, while here, we need $\modal T$, when $T:\Type^i$ to live in a
possibly higher universe $\Type^j$. For modalities on whole $\Type$,
we checked that all properties are still satisfied (see
\url{https://github.com/KevinQuirin/HoTT/extended_modalities/} for the
formalization).
